Was Devon Allen Unjustly Disqualified at the 2022 World Track and Field Championships?

### 2023-03-21 Manuscript/manuscript.tex
comments on styles

@@

>>>>

\jy{Avoid references in abstract.}

\jy{The bib file needs quality control. The bib keys need to have a consistent
  style. I suggest using the keys from google scholar.}

\jy{Practice my writing tips in the stat-wriging notes: chapter 2 on
  latex. E.g., no vertical/horizontal lines in professional tables. Use the
  tables in my template.}

@@

\jy{Not a good opening. Could start by telling the story, recapping the major
  events and discussions on the internet. Then dig into the relevant
  literature. Finally outline the contributions of this work.
}
